### 2019-02-01 results.tex
MZ- Update MSE and ACCU numbers

% \textcolor{blue}{Describe what these are in a couple of sentences.}
In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for this Prophet are listed in the table~\ref{tab:prophet_para}. For each cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and $n$ is the number of data points. The application returns the average MSE across cross validations. 
%Using a the model trained by default parameter setting, this average MSE metric is 0.284.

\begin{table}[t]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|} 
\hline
\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
\hline
grow & linear & [linear, logistic] \\
\hline
changepoint prior scale & 0.05 & [0.05, 0.5] \\
\hline
holidays prior scale & 10 & [1, 5, 10] \\
\hline
seasonality prior scale & 0.5 & [0.1, 0.5] \\
\hline
fourier order & 10 & [5, 10, 15, 20] \\
\hline
seasonality mode & additive & [additive, multiplicative] \\
\hline
interval width & 0.8 & [0.5, 0.8] \\
\hline
\end{tabular}}
\caption{Default hyperparameters for Prophet. The default value and tuning options are listed. 
\label{tab:prophet_para}}
\vspace{-0.2in}
\end{table}

Multi-Regression is a regression application 
developed by the authors of 
an IoT project~\cite{iot-cpu} that
predicts outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures (e.g. for use in 
precision agriculture applications such as irrigation control and frost protection).
The training dataset consists of eight input time series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

@@

For these applications (XGBoost, SVC, and Neural Network), 
we use a labeled dataset for training, testing, and evaluation from a separate
project (name and citation ommitted for blind review).
The dataset contains
measurements of individual citrus fruit (e.g. oranges, mandarins, lemons, etc.) 
taken by a fruit sorting and grading device (using a large number of sensors).  
The measurements (i.e. features)
include size, shape, weight, color, diameter, flatness, among other characteristics,
for each fruit.  The label indicates which field each fruit was harvested from.  
The applications train a model on a random subset of the data.  
They then use this model to predict the field
from which each fruit originates. They compute classification accuracy score as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the prediction class, $Y_i$ is the true class, $n$ is the number of samples and 1(x) is the indicator function. XGBoost also computes MSE for its regression task on the same datasets. The dataset has been filtered to remove correlated features (those with an absolute value of the Pearson correlation coefficient greater than 0.8) and outliers. 
%The dataset has also been balanced by downsampling one target whose number 
%greatly exceeds other ones. 
The resulting dataset contains 33926 rows (individual fruit) distributed evenly across 5 targets, and each row has 18 features.

@@

%Seneca downloads the dataset from AWS S3 for each function invocation.
%It then randomly indexes the data set and splits it into two.  
For these applications (XGBoost, SVC, and Neural Network), 
Seneca splits the dataset and uses 80\% and 20\% for testing.
For Neural Network and XGBoost, we also consider other splits
that requires less data for training: \textcolor{blue}{list them here once we finish
the additional results}. 
%This setup also means that each Seneca function
%considers a different training and testing set during hyperparameter tuning.

@@

\subsection{Empirical Methodology}
To evaluate Seneca, we measure tuning performance, application execution time, and monetary cost.
For tuning performance, we use mean squared error (MSE) for regression tasks 
and percentage accuracy for
classification tasks. The default configuration that we 
consider for each application is described above.
We report results for the default, the best (Seneca's recommendation), 
and the worst performing configurations.  Seneca considers all possible combinations 
of the hyperparameter settings specified in the configuration, uses them
to train, test, and evaluate models for each. 
The default results represents a configuration that a novice or first time 
user might employ when using these applications
as a "black box".  The worst performing scenario shows how bad the results can be
when parameters are poorly tuned.  Finally, the best configuration 
is the one that results from tuning they hyperparameters for the test/train split
that Seneca considers.

@@

We also experiment with different memory configurations for Seneca functions in AWS Lambda.  
We evaluate
the performance and cost of allocating the maximum memory for each and for automatically optimizing 
memory use using Seneca. We assume that all combinations hyperparameter settings use the 
same maximum amount of memory across functions; we 
have verified that this assumption holds for the applications and datasets that
we consider herein.
We plan to consider applications for which hyperparameter settings require 
different maximum amounts of memory as part of future work.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
& Prophet & Multi-Regression & XGBoost\\
\hline
\# of Combinations & 384 & 255 & 768\\
\hline
\hline
Default MSE & 0.284 & 11.446 & 0.119 \\
\hline
Worst MSE & 1.266 & 43.752 & 8.069 \\
\hline
Best MSE (Seneca) & 0.220 & 9.621 & 0.049 \\
\hline
%percent difference between default and best 26.07%, 15.94%, 67.30%
%percent difference between worst and best 82.63%, 78.01%, 95.52%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.4]{mse}
\end{tabular}
\caption{Combination count and MSE for the default, 
best (Seneca's recommendation), 
and worst hyperparameter configurations for the three regression applications. 
For the MSE  values (rows 3-5), lower is better.
\label{tab:mse}}
\end{table}

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{box_plot_mse}
\caption{The box plot of MSE from the three regression applications 
across the hyperparameter tuning search space. 
The red notch shows the MSE from the default configuration. 
The colored diamonds are outliers beyond two interquartile ranges. 
Lower MSE values are better.
\label{fig:box_plot_mse}}
\vspace{-0.2in}
\end{figure}

We first evaluate Seneca using the three regression applications: 
Prophet, Multi-Regression, and XGBoost (regression task). 
Table ~\ref{tab:mse} shows the size of the hyperparameter search space (number of configurations
considered) and the mean squared error (MSE)
for each of the regression applications that we consider (columns 3-5).
The first row of data is 
 the number of hyperparameter configurations that Seneca considers in search space of each. 
The last three rows show the MSE for the default, worst, and best performing 
hyperparameter configuation reported by Seneca (lower is better).  
Seneca reduces MSE by 26\%, 16\%, and 67\%, for Prophet, Multi-Regression, and XGBoost,
respectively, for the datasets and training methodologies that we consider.
Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 96\%, respectively.

Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better)
for these applications 
for the entire hyperparameter 
search space. The central rectangle covers the interquartile range (IQR), 
which is defined as the range of data 
points from first quartile to third quartile (Q3 - Q1). 
The upper whisker extends to the last datum less 
than \texttt{$(Q3 + 2 * IQR)$} and the lower whisker extends to the first datum greater 
than \texttt{$(Q1 - 2 * IQR)$}. The data points beyond the whiskers are considered outliers 
and are plotted as colored diamonds. The red notch identifies the MSE that results from training 
the model using the default settings of hyperparameter. 
The difference between red notch of lowest data 
point is the improvement brought about by the use of Seneca. 
The red notch marks the MSE of the default hyperparameterization.
Each is located near the 
From the location of red notch, we can see the MSE metrics 
first quartile value indicating that there is significant 
potential room for improvement in MSE. The box plot also illustrates 
that the best MSE of Prophet and multivariate regression are among the outliers, 
indicating that a comprehensive search is critical to finding the best configurations. 
%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE for the range of configurations and how they change across applications. Include any insights that the boxplots add.}

%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance %%%%%%%%%%%%%%%%%%%%%%%%%
We next empirically evaluate the tuning performance of Seneca for the three
classification applications: XGBoost (classification), SVC, and Neural Network.
Figure~\ref{fig:accuracy} presents the accuracy percentage (higher is better) 
reported by each application (3 left-most columns) 
for the default, worst, and best hyperparameter tuning 
configurations (data rows 2-4) reported by Seneca.  
The first row of the table
reports the number of configurations that Seneca considers in its search space.
Seneca increases accuracy by 84\%, 84\%, and 80\%, for XGBoost (classification), 
SVC, and Neural Network applications,
respectively, for the datasets and training methodologies that we consider.
Verses the worst case, Seneca improves accuracy by 86\%, 86\%, and 85\%, respectively.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
& XGBoost & SVC & Neural Network\\
\hline
\# of Combinations & 768 & 512 & 432\\
\hline
\hline
Default MSE&2.42\%&3.93\%&6.51\%\\
\hline
Worst MSE&0.00\%&2.04\%&1.72\%\\
\hline
Best MSE (Seneca) &86.07\%&87.76\%&86.34\%\\
\hline
%percent difference between default and best 83.65%, 83.84%, 79.83%
%percent difference between worst and best 86.07%, 85.73%, 84.63%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.38]{accuracy}
\end{tabular}
\caption{Combination count and accuracy reported for the 
default, best (Seneca's recommendation), and worst hyperparameter configurations for 
the three classification applications.  
For the accuracy  values (rows 3-5), higher is better.
\label{fig:accuracy}}
%\vspace{-0.2in}
%\end{figure}
\end{table}

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{box_plot_accuracy}
\caption{The box plot of accuracy metric 
from the classification applications for the entire hyperparameter tuning search space. 
The red notch indicates the accuracy metric from the trained model using the default configuration. 
The colorful diamonds are outliers beyond two interquartile ranges. Higher accuracy values are better.
\label{fig:box_plot_accuracy}}
% \vspace{-0.2in}
\end{figure}

Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
for the entire hyperparameter search space for each classification
application.  The central rectangle covers from first quartile to third quartile 
(Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. 
The red notch indicates the accuracy metric from the model trained using the default 
settings and colored diamonds show outliers beyond the whiskers.
For both types of applications (regression and classification), Seneca significantly
improves tuning performance over the default and worst case configurations for the 
datasets and training methodologies that we consider.

@@

We next analyze the monetary cost introduced by Seneca. 
We consider two scenarios for its implementation.
First, we configure each lambda function to use the maximum amount
of memory allowed by AWS Lambda (3008 MB).  Second, we employ Seneca's memory optimization,
which automatically detects and configures the amount of memory needed by each function.
Because memory impacts both cost and execution time (total latency of Seneca 
hyperparameter tuning), we present empirically evaluate both 
in this subsection.  For each, we only include XGBoost once since its 
performance profile is the same
regardless of whether we are using regression or classification.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 13 & 7 & 3 & 15 & 14 \\
\hline
Cost of Tuning (\$) &0.406 & 0.220 & 0.075 & 0.213 & 0.161 \\
\hline
\end{tabular}
\caption{Monetary cost of using Seneca for hyperparameter 
tuning when configured to use the maximum amount of memory(3008MB) 
possible for each function invocation. 
\label{tab:cost_max_memory}}
\vspace{-0.2in}
\end{table}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 33 & 17 & 9 & 17 & 14 \\
\hline
Cost of Tuning (\$) &0.325 & 0.120 & 0.043 & 0.141 & 0.130 \\
\hline
Cost of optimization (\$) &0.033 & 0.014 & 0.003 & 0.010 & 0.008 \\
\hline
Total Cost (\$) &0.358 & 0.134 & 0.045 & 0.151 & 0.138 \\
\hline
\end{tabular}
\caption{Seneca  Memory  Optimization:  The  monetary  cost  of 
using Seneca for hyperparameter tuning when the amount of memory  
used  for  each  function  invocation  is  automatically
inferred and set by Seneca.
\label{tab:cost_optimized}}
\vspace{-0.2in}
\end{table}

Tables~\ref{tab:cost_max_memory} and~\ref{tab:cost_optimized} show the results with and without 
the Seneca memory optimization, respectively. In both tables, the five columns identify the 
benchmark applications and the first row is the total execution time in minutes for 
Seneca's hyperparameter tuning for the corresponding application.  
The second row shows the total monetary cost of tuning each application using Seneca;
for Table~\ref{tab:cost_max_memory} (unoptimized) this is the Total Cost of using Seneca.

To perform the memory optimization (Table~\ref{tab:cost_optimized}), 
Seneca requires additional runs of the application
and as such, introduces additional cost.  This cost is shown for each application in 
the third row.  Total Cost is the sum of rows 2 and 3 in this table and is the 
total cost of using Seneca with its memory optimization.

By reducing the amount of memory used, Seneca reduces total cost.  
However by doing so, Seneca also 
increases the total time it requires to perform hyperparameter tuning (Exec time in minutes 
in row 1 of both tables) for some applications.  
On average, the Seneca memory optimization increases latency by 73\% across applications.
By reducing memory use however, Seneca reduces the monetary cost by 83\% across applications 
even with the added overhead of optimization.

%%%%%%%%%%%%% everything below this point is commented out %%%%%%%%%%%%%%

@@

\ignore{ %%%%%%%%%% all of this data already appears in the tables above! %%%%%%%%%%%%%
\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{Cost_analysis}
\caption{ The cost analysis of Seneca with (Opt) and without (No Opt) the use of its memory optimization. 
By reducing the memory use of each, Seneca reduces the monetary cost of hyperparameter tuning by \textcolor{blue}{X\% on average, across these applications.  *compute and Fill this X in*.}
\textcolor{blue}{Change the legend as follows: change "Tuning at Max Memory" to "No Opt"; change "Function Optimization" to "Opt cost"; change "Tuning" to "Opt". If you can put legend in this order: Opt, Opt cost, No Opt} 
\label{fig:cost_analysis}}
\vspace{-0.2in}
\end{figure}

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{Latency_analysis}
\caption{Latency of Seneca with (Opt) and without (No Opt) memory optimization, for each application. As Seneca reduces memory use (and cost), it also extends the execution time of the functions (and thus total tuning time, i.e., the latency of Seneca) by Y\% on average across applications \textcolor{blue}{compute and fill in Y here.}
\textcolor{blue}{Change the legend as follows: change "Optimized Memory" to "Opt"; change "Maximum Memory" to "No Opt"; Make sure that Opt stays green and change No Opt to be red (same as above graph)} 
\label{fig:latency_analysis}}
\vspace{-0.2in}
\end{figure}

@@

}

>>>>

% \textcolor{blue}{Describe what these are in a couple of sentences.}
In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for this application are listed in the table~\ref{tab:prophet_para}. For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points. Then the application returns the average MSE of all cross validation. Based on the model trained by default parameter setting, this average MSE metric is 0.284.

\begin{table}[t]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|} 
\hline
\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
\hline
grow & linear & [linear, logistic] \\
\hline
changepoint prior scale & 0.05 & [0.05, 0.5] \\
\hline
holidays prior scale & 10 & [1, 5, 10] \\
\hline
seasonality prior scale & 0.5 & [0.1, 0.5] \\
\hline
fourier order & 10 & [5, 10, 15, 20] \\
\hline
seasonality mode & additive & [additive, multiplicative] \\
\hline
interval width & 0.8 & [0.5, 0.8] \\
\hline
\end{tabular}}
\caption{The selected configurable hyperparameters of Prophet. The default value and tuning options are listed. 
\label{tab:prophet_para}}
\vspace{-0.2in}
\end{table}

Multi-Regression is a regression application 
from an IoT project~\cite{iot-cpu} that was developed by the authors
to predict outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures (e.g. for use in 
precision agriculture applications such as irrigation control and frost protection).
The training dataset consists of eight input time series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

@@

For these applications (XGBoost, SVC, and Neural Network), 
we use a labeled dataset for training, testing, and evaluation from 
this project~\cite{iot-cpu}. The dataset contains
measurements from individual citrus fruit (e.g. oranges, mandarins, lemons, etc.) 
taken by a fruit sorting and grading device (using a large number of sensors).  
The measurements (i.e. features)
include size, shape, weight, color, diameter, flatness, among other characteristics,
for each fruit.  The label indicates which field the fruit was harvested from.  
The applications train a model on a random subset of the data.  
They then use this model to predict the field
%%<<<<<<< HEAD
%%from which each fruit originates.  They compute classification accuracy 
%%as \textcolor{blue}{finish this.}.  XGBoost also computes MSE for its regression task
%%on the same datasets.  The dataset has been filtered authors to remove correlated 
%%features (those with an absolute value of the Pearson correlation coefficient greater than 0.8).  
%%The resulting dataset contains 218150 rows (individual fruit) each with 19 features. 
from which each fruit originates. They compute classification accuracy score as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the prediction class, $Y_i$ is the true class, n is the number of samples and 1(x) is the indicator function. XGBoost also computes MSE for its regression task on the same datasets. The dataset has been filtered to remove correlated features (those with an absolute value of the Pearson correlation coefficient greater than 0.8). The dataset has also been balanced by downsampling one target whose number greatly exceeds other ones. The resulting dataset contains 33926 rows (individual fruit) distributed evenly to 5 targets and each row has 18 features.

@@

%Seneca downloads the dataset from AWS S3 for each function invocation.
%It then randomly indexes the data set and splits it into two.  
For these applications (XGBoost, SVC, and Neural Network), we consider three split scenarios for training and testing: 80\%-20\%, 20\%-80\% and 0.1\%-99.9\%. As the proportion of training data decreases, the performance of classifier degrades accordingly and we argue that Seneca is able to eke out improvement even with very limited training data.
%\textcolor{blue}{list them here once we finish the additional results} 
%This setup also means that each Seneca function
%considers a different training and testing set during hyperparameter tuning.

@@

\subsection{Empirical Methodology}
To evaluate Seneca, we measure tuning performance, application execution time, and monetary cost.
For tuning performance, we use mean squared error (MSE) for regression tasks 
and percentage accuracy for
classification tasks. The default configuration that we 
consider for each application is described above.
We report results for the default, best (Seneca's recommendation), 
and worst performing configurations.  Seneca computes all possible combinations 
of the hyperparameter settings specified in the configuration to extract each of these results.
The default results represents those that a novice or first time 
user might employ when using these applications
as a "black box".  The worst performing scenario shows how bad the results can be
when parameters are poorly tuned.  Finally, the best is the upper bound on what is possible from 
tuning the hyperparameters (e.g. using expert knowledge or Seneca).

@@

We also experiment with different memory configurations for Seneca functions in AWS Lambda.  
We evaluate
the performance and cost of allocating the maximum memory for each and for automatically optimizing 
memory use using Seneca. We assume that all combinations hyperparameter settings use the 
same maximum amount of memory across functions; we 
have verified that this assumption holds for the applications and datasets we consider.
We plan to consider applications for which hyperparameter settings require 
different maximum amounts of memory as part of future work.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
& Prophet & Multi-Regression & XGBoost\\
\hline
\# of Combinations & 384 & 255 & 768\\
\hline
\hline
Default MSE & 0.284 & 11.446 & 0.119 \\
\hline
Worst MSE & 1.266 & 43.752 & 8.98 \\
\hline
Best MSE (Seneca) & 0.220 & 9.621 & 0.044 \\
\hline
%percent difference between default and best 26.07%, 15.94%, 67.30%
%percent difference between worst and best 82.63%, 78.01%, 95.52%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.4]{mse}
\end{tabular}
\caption{Combination count and MSE for the default, best (Seneca's recommendation), and worst hyperparameter configurations for the three regression applications. 
For the MSE  values (rows 3-5), lower is better.
\label{tab:mse}}
\end{table}

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{box_plot_mse_2}
\caption{The box plot of MSE metric from three regression applications in the entire hyperparameter tuning search space. The red notch shows the MSE from the default settings. The colored diamonds are outliers beyond two interquartile ranges. Lower MSE values are better.
\label{fig:box_plot_mse}}
\vspace{-0.2in}
\end{figure}

We first evaluate Seneca using the three regression applications: 
Prophet, Multi-Regression, and XGBoost (regression task). 
Table ~\ref{tab:mse} shows the size of the hyperparameter search space (number of configurations
considered) and the mean squared error (MSE)
for each of the regression applications that we consider (columns 3-5).
The first row of data is 
 the number of hyperparameter configurations in the search space of each. 
The last three rows show the MSE for the default, worst, and best performing 
hyperparameter configuation reported by Seneca (lower is better).  
Note that Seneca's recommendation is the best performing configuration.
Seneca reduces MSE by 26\%, 16\%, and 63\%, for Prophet, Multi-Regression, and XGBoost,
respectively, for the datasets and training methodologies that we consider.
Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 99\%, respectively.

Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better)
for these applications 
for the entire hyperparameter 
search space. The central rectangle covers the interquartile range (IQR), 
which is defined as the range of data 
points from first quartile to third quartile (Q3 - Q1). 
The upper whisker extends to the last datum less 
than \texttt{$(Q3 + 2 * IQR)$} and the lower whisker extends to the first datum greater 
than \texttt{$(Q1 - 2 * IQR)$}. The data points beyond the whiskers are considered outliers 
and are plotted as colored diamonds. The red notch identifies the MSE that results from training 
the model using the default settings of hyperparameter. The difference between red notch of lowest data 
point is improvement brought about through the use of Seneca. From the location of red notch, we can see the MSE metrics from default configuration in three applications are close to the first quartile value, meaning the potential room for improvement is about 75\% over the range of MSE metric. The box plot also illustrates that the best MSE of Prophet and multivariate regression are among outliers, where a comprehensive search is very critical to find the best configurations. 
%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE for the range of configurations and how they change across applications. Include any insights that the boxplots add.}

%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance %%%%%%%%%%%%%%%%%%%%%%%%%
We next empirically evaluate the tuning performance of Seneca for the three
classification applications: XGBoost (classification), SVC, and Neural Network.
Table~\ref{tab:accuracy} presents the accuracy percentage (higher is better) 
reported by each application (3 right-most columns) 
for the default, worst, and best hyperparameter tuning configurations under three training and testing split scenarios reported by Seneca.  
In the 80/20 percent split case, Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost (classification), 
SVC, and Neural Network applications,
respectively.
Verses the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%, respectively.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{80\%-20\%} & XGBoost & SVC & Neural Network\\
\hline
\hline
Default Accuracy & 95.70\% & 21.77\% & 84.23\%\\
\hline
Worst Accuracy&0.00\%&7.53\% & 19.19\%\\
\hline
Best Accuracy (Seneca) &99.13\% & 83.29\% & 84.76\%\\
\hline
\hline
\textbf{20\%-80\%} & XGBoost & SVC & Neural Network\\
\hline
Default Accuracy & 95.07\% & 21.31\% & 55.44\%\\
\hline
Worst Accuracy&0.00\% & 9.42\% & 19.55\%\\
\hline
Best Accuracy (Seneca) & 98.68\% & 43.61\% & 60.89\%\\
\hline
\hline
\textbf{0.1\%-99.9\%} & XGBoost & SVC & Neural Network\\
\hline
Default Accuracy & 86.37\% & 20.02\% & 20.00\%\\
\hline
Worst Accuracy & 0.00\% & 19.99\% & 19.79\%\\
\hline
Best Accuracy (Seneca) & 89.14\% & 55.79\% & 29.99\%\\
\hline

%percent difference between default and best 83.65%, 83.84%, 79.83%
%percent difference between worst and best 86.07%, 85.73%, 84.63%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.38]{accuracy}
\end{tabular}
\caption{The Accuracy reported for the 
default, best (Seneca's recommendation), and worst hyperparameter configurations for 
the three classification applications under three train/test split scenarios.  
For the accuracy values in the table, higher is better.
\label{tab:accuracy}}
%\vspace{-0.2in}
%\end{figure}
\end{table}

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{box_plot_accuracy}
\caption{The box plot of accuracy metric from three classification applications for the entire hyperparameter tuning search space. The red notch indicates the accuracy metric from the trained model using default settings. The colorful diamonds are outliers beyond two interquartile ranges. Higher accuracy values are better.
\label{fig:box_plot_accuracy}}
% \vspace{-0.2in}
\end{figure}

Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
for the entire hyperparameter search space for each classification
application.  The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
For both types of applications (regression and classification), Seneca significantly
improves tuning performance over the default and worst case configurations for the 
datasets and training methodologies we consider.

@@

We next analyze the monetary cost introduced by Seneca. 
We consider two scenarios for its implementation.
First, we configure each lambda function to use the maximum amount
of memory allowed by AWS Lambda (3008 MB).  Second, we employ Seneca's memory optimization 
which automatically detects and configures the amount of memory needed by each function.
Because memory impacts both cost and execution time (total latency of Seneca hyperparameter tuning), 
we present empirically evaluate both 
in this subsection.  For each, we only include XGBoost once since its 
performance profile is the same
regardless of whether we are using regression or classification.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 24.96 & 4.18 & 17.48 & 0.91 & 2.49 \\
\hline
Cost of Tuning (\$) & 0.722 & 0.121 & 0.5 & 0.023 & 0.072 \\
\hline
\end{tabular}
\caption{ Monetary cost of using Seneca for hyperparameter tuning when configured to use the maximum amount of memory (3008 MB) possible for each function invocation. 
\label{tab:cost_max_memory}}
\vspace{-0.2in}
\end{table}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 38.7 & 8.72 & 29.07 & 0.91 & 3.17 \\
\hline
Cost of Tuning (\$) &0.62 & 0.086 & 0.354 & 0.007 & 0.056 \\
\hline
Cost of optimization (\$) &0.033 & 0.014 & 0.003 & 0.010 & 0.008 \\
\hline
Total Cost (\$) &0.653 & 0.1 & 0.357 & 0.016 & 0.064 \\
\hline
\end{tabular}
\caption{ Seneca  Memory  Optimization:  The  monetary  cost  of using Seneca for hyperparameter tuning when the amount of memory  used  for  each  function  invocation  is  automatically inferred and set by Seneca.
\label{tab:cost_optimized}}
\vspace{-0.2in}
\end{table}

Tables~\ref{tab:cost_max_memory} and~\ref{tab:cost_optimized} show the results with and without 
the Seneca memory optimization, respectively. In both tables, the five columns identify the 
benchmark applications and the first row is the total execution time in minutes for 
Seneca's hyperparameter tuning for the corresponding application.  
In table~\ref{tab:cost_max_memory}, the second row is total cost of tuning when Seneca's 
lambda functions are configured to use the maximum amount of memory (3008 MB), whereas table~\ref{tab:cost_optimized} demonstrates the additional cost of optimization in the third row 
and total cost on fourth row.
% \textcolor{blue}{See my notes to fix the tables in the caption of these figures.}

@@

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{Cost_analysis_2}
\caption{ The cost analysis of Seneca with (Opt) and without (No Opt) the use of its memory optimization. 
By reducing the memory use of each, Seneca reduces the monetary cost of hyperparameter tuning by \textcolor{blue}{X\% on average, across these applications.  *compute and Fill this X in*.}
\textcolor{blue}{Change the legend as follows: change "Tuning at Max Memory" to "No Opt"; change "Function Optimization" to "Opt cost"; change "Tuning" to "Opt". If you can put legend in this order: Opt, Opt cost, No Opt} 
\label{fig:cost_analysis}}
\vspace{-0.2in}
\end{figure}

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{Latency_analysis_2}
\caption{Latency of Seneca with (Opt) and without (No Opt) memory optimization, for each application. As Seneca reduces memory use (and cost), it also extends the execution time of the functions (and thus total tuning time, i.e., the latency of Seneca) by Y\% on average across applications \textcolor{blue}{compute and fill in Y here.}
\textcolor{blue}{Change the legend as follows: change "Optimized Memory" to "Opt"; change "Maximum Memory" to "No Opt"; Make sure that Opt stays green and change No Opt to be red (same as above graph)} 
\label{fig:latency_analysis}}
\vspace{-0.2in}
\end{figure}

@@
